\documentclass{article}

\usepackage{titlesec}
\usepackage{titling}
\usepackage{enumitem}
\usepackage{ragged2e}
\usepackage[margin=0.25in]{geometry}
\usepackage{multicol}
\usepackage{parskip}


\author{Ali Al Temimi}


\titleformat{\section}
{\bfseries\huge}
{}
{0em}
{}[\titlerule]

\titleformat{\subsection}
{\bfseries\large}
{}
{0em}
{}

\titleformat{\subsubsection}
{\bfseries\raggedleft}
{}
{0em}
{}


\pagenumbering{gobble}
\renewcommand{\maketitle}{
\begin{center}
    {\huge\bfseries
    \theauthor}
    {\Large \\ali@altemimi.xyz $\bullet$ 07930408174}
    \vspace{-4em}
\end{center}
}

\begin{document}
    \maketitle
\section{}
Computer Science graduate from the University of Hull, with interest in Software Development, Electronics and Fullstack Web development. 
    \begin{multicols}{2}
        \section{Education}
        \subsection{University of Hull (September 2018 - June 2021) First Class Honours}
        \subsubsection{BSc Computer Science}
        \begin{description}
            \item[$\bullet$]Advanced Programming - Developed a highly efficient Sudoku solver in C++ (93\%)
            \item[$\bullet$]Artificial Intelligence - Developed Genetic Algorithm for an existing Neural Network in C\# (72\%)
            \item[$\bullet$]Object-Oriented Programming - Created the game "Uno" in C\# (60\%)
            \item[$\bullet$]Electronics and Interfacing - Developed an assortment of small software for an Arduino microcontroller (69\%)
            \item[$\bullet$]System Analysis, Design and Process - Group project to design and develop a piece of software and go through the whole software development process using the Agile methodology (71\%)
            \item[$\bullet$]Agile Software Development - Developed a Forum website in a group using SCRUM and the Agile methodology (70\%)
        \end{description}
        \subsection{Hull College(September 2016 - June 2018) Grade - D*DD}
        \subsubsection{Level 3 Extended Certificate in IT}
        \begin{description}
            \item[$\bullet$]3D Modeling - Designed and Created Two 3D models in Blender
            \item[$\bullet$]Website Production - Designed and Developed an Educational Website that covers Bronze age to Late Medival history 
            \item[$\bullet$]Database - Developed dashboards together with a team of students for a booking system that was created in Microsoft Access. 
        \end{description}
    \section{Experience}
        \subsection{Smash Crab Studios (September 2015 - December 2015)} 
        \begin{description}
            \item[$\bullet$]We worked on developing abilities for a mobile game.
            \item[$\bullet$]Worked on a replica of the Snake game within a group of other students in Unity. 
            \item[$\bullet$]Used git and source control to make a game in a team with Unity Game Engine.
        \end{description}
        \subsection{Fantasticon (September 2016 - September 2016)} 
        \begin{description}
            \item[$\bullet$]Worked with team members to ensure that the venues in the event had everything that they needed.
            \item[$\bullet$]Coordinated with team members the most efficient placement of the volunteers to be easily called for if needed.
        \end{description}
        \columnbreak
    \section{Projects}
    \subsection{EEG Controlled Prostetic (Final Year Dissertation)}
    Used Python to develop software that can control a 3D printed prosthetic by reading real-time brain data. 
    The software mimics an EEG brain-reading device and outputs the data similarly to what an EEG device would. 
    The other part of the software reads in the data with the help of Sockets; 
    the software then processes it into a graph using Matplotlib. 
    \section{Technical Skills}
        \subsection{Programing Languages}
        \subsubsection{Python}
        \subsubsection{C++}
        \subsubsection{C\#}
        \subsubsection{JavaScript}
        \subsection{Markup Languages}
            \subsubsection{HTML}
            \subsubsection{CSS}
            \subsubsection{LaTeX}
        \subsection{Tools}
            \subsubsection{Git}
            \subsubsection{Arduino}
            \subsubsection{Adobe CC}
            \subsubsection{Fusion 360}
            \subsubsection{Blender}
        \subsection{Languages}
            \subsubsection{Swedish}
            \subsubsection{Arabic}
            \subsubsection{English}
    \end{multicols}
\end{document}
